---
title: "Data Analysis Lab"
output: pdf_document
---

##### Assignment Instructions

Complete all questions below. After completing the assignment, knit your document, and download both your .Rmd and knitted output. Upload your files for peer review. 

For each response, include comments detailing your response and what each line does. 

---
```{r}
# loading tidyverse and nycflights
library(tidyverse)
library(nycflights13)
```

##### Question 1. 

Using the nycflights13 dataset, find all flights that departed in July, August, or September using the helper function between(). 

```{r question-1-response}
# creating a pipe that filters flights between months July to September
flights |>
  filter(between(month, 7, 9))
```


#### Question 2. 

Using the nycflights13 dataset sort flights to find the 10 flights that flew the furthest. Put them in order of fastest to slowest.

```{r question-2-response}
flights |>
  # find the flights that flew furthest
  arrange(desc(distance)) |>
  # take the top 10 flights
  slice_head(n = 10) |>
  # sort these flights from fastest to slowest
  arrange(desc(distance / air_time))
```

#### Question 3. 

Using the nycflights13 dataset, calculate a new variable called "hr_delay" and arrange the flights dataset in order of the arrival delays in hours (longest delays at the top). Put the new variable you created just before the departure time.Hint: use the experimental argument .before. 

```{r question-3-response}
flights |>
  # create new variable hr_delay, putting this before dep_time
  mutate(hr_delay = arr_delay / 60, .before = dep_time) |>
  # arrange dataset from longest to shortest delays
  arrange(desc(hr_delay))
```

##### Question 4.

Using the nycflights13 dataset, find the most popular destinations (those with more than 2000 flights) and show the destination, the date info, the carrier. Then show just the number of flights for each popular destination.

```{r question-4-response}
# find the most popular destinations with more than 2000 flights
popular_destinations <- flights |>
  # group the dataset by destinations
  group_by(dest) |>
  # filter thos out, with more than 2000 flights
  filter(n() > 2000) |>
  # select destination, date, carrier
  select(dest, year, month, day, carrier)

# show results
popular_destinations

# show just the numbers of flights for each popular destination
popular_destinations |>
  count(dest) |>
  arrange(desc(n))

```

#### Question 5. 

Using the nycflights13 dataset, find the flight information (flight number, origin, destination, carrier, number of flights in the year, and percent late) for the flight numbers with the highest percentage of arrival delays. Only include the flight numbers that have over 100 flights in the year.

```{r question-5-response}
flights |>
   # group dataset by flight number, origin, destination, carrier
  group_by(flight, origin, dest, carrier) |>
  # summarise flights per year and calculate percent late
  summarise(
    num_flights = n(),
    percent_late = mean(arr_delay > 0, na.rm = TRUE) * 100
  ) |>
  # filter out flight numbers with over 100 flights per year
  filter(num_flights > 100) |> 
  # arrange from highest to lowest percentage of arrival delays
  arrange(desc(percent_late)) |>
  # select required columns
  select(flight, origin, dest, carrier, num_flights, percent_late)
```